### 2018-07-04 report.tex

\subsection{Data generation}

\subsection{Data loading}

\subsection{Database search}

@@

>>>>

\subsection{Data generation and loading}

The proteome benchmark dataset from \cite{Cox2014} was reanalysed starting at the output RAW files available at the PRIDE repository \footnote{\href{https://www.ebi.ac.uk/pride/archive/projects/PXD000279}{https://www.ebi.ac.uk/pride/archive/projects/PXD000279}}. Briefly, the \textit{Homo sapiens} and \textit{E. coli (strain K12)} proteomes were mixed in 1:1 and 1:3 proportions, with 3 replicates for each combination. Moreover, each of the 3 replicates of the 2 conditions was analysed in 24 fractions. This experimental setting thus generated a total of 2*3*24=144 RAW files. The ThermoRawFileParser CITE THERMORAWFILEPARSER program was used to convert RAW files to the open format MGF (Mascot Generic Format) that can be used by the tools following the pipeline.

\subsection{Decoy database preparation and search}

The spectra contained in the MGF files obtained in the previous step were loaded onto the MS-GF+ search engine CITE using the SearchGUI \texttt{SearchCLI} CITE utility. The search parameters were set using the \texttt{IdentificationParametersCLI}. In order to account for potential post-translational modifications, the search was conducted allowing for the following variable modifications: oxidation of M and deamidation of N and Q. Moreover, C carbamidomethylation was set as fixed modification during the search. The enzyme was set to semispecific Trypsin, allowing for a non-tryptic cleavage on any side of the peptide. Up to two missed cleavages were allowed. The precursor tolerance was 10 ppm and the fragment tolerance 0.5 Da.

The database was created by combining the Uniprot proteomes for \textit{E. coli (strain K12)} (UP000000625) and \textit{Homo sapiens} (UP000005640), downloaded in June 2018. The decoy database was created using the \texttt{FastaCLI} utility in SearchGUI by reversing all sequences in the original database.

@@

Relative quantification was performed using the MSqRob utility by passing the peptide summary file from moFF. Prior to quantification, the data was preprocessed using the \texttt{preprocess\_MSnSet()} function. In a nutshell, (I) MS1 apex intensities were $log_2$ transformed, (II) peptides belonging to protein groups that contained one or more proteins that were also present in a smaller protein group CITE MAIN MSQROB were discarded, and (III) protein groups with only 1 peptide were dropped. Intensity normalisation was not performed as a systematic bias in intensities is indeed expected for all \textit{E. coli} peptides from samples where the \textit{E. coli}proteome was 3 times more abundant.

One preprocessing is done, a ridge regression model with Huber weights and empirical Bayes estimation of the protein variance was fit to every protein individually. The significance of the treatment effect differences was assessed through a Student\textquotesingle s T test, implemented in the \texttt{test.contrast()} function.

The result of this step was a table where the $log_2(FC)$ estimate, together with test statistics are returned for every protein group.
